---
title: "WRBTrends"
output: rmarkdown::html_vignette
description: Documentation to support the use of the WRBTrends package. This package contains functions used by the Water Resources Branch to process various data streams into a format from which trend statistics can be calculated.
vignette: >
  %\VignetteIndexEntry{WRBTrends}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(WRBTrends)
```


This vignette introduces the WRBTrends package of functions and aims to support its use. The functions described below can be used to process and analyse data.frames and lists of data.frames/tibbles containing time-series data, including repeated snowpack surveys, point measurements of various types, laboratory analyses, and water level readings.

In addition, the package contains functions to facilitate trend analyses. In particular, it contains functions to parse external documents containing grading and time-series identifier labels, using this information to download and format time-series data from Aquarius, EQWin, the Snow Survey Access database, ECCC, and Excel workbooks.

The heart of the trend analysis functions are the trend, Kendall, and rkt packages. Refer to their vignettes and help files if you require more information about the mechanics of trend and slope calculations.

***


### Example Data for {#data}


Two example datasets are provided:

1. A data.frame containing the WRB's snow survey measurements at all currently active stations, from their measurement start date to 2021. This data has been modified from the standard Microsoft Access output to allow for direct use with these functions.
```{r}
data("activeStations")
```

1. A list of data.frames. One data.frame exists for every station active in 2021 and contains only the peak snow water equivalent measurement for each year.

```{r}
data("ActiveHighSWE")
```





***

